Online appendix for "Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2024-09-22 manuscript/appendix.qmd
Use homebrew ghostscript

```{r tikz-stuff, include=FALSE}
if (Sys.info()["sysname"] == "Darwin") {
  # Necessary for using dvisvgm on macOS
  # See https://www.andrewheiss.com/blog/2021/08/27/tikz-knitr-html-svg-fun/
  Sys.setenv(LIBGS = "/usr/local/share/ghostscript/9.53.3/lib/libgs.dylib.9.53")
}

>>>>

```{r tikz-stuff, include=FALSE}
if (Sys.info()["sysname"] == "Darwin") {
  # Necessary for using dvisvgm on macOS
  # See https://www.andrewheiss.com/blog/2021/08/27/tikz-knitr-html-svg-fun/
  Sys.setenv(LIBGS = "/opt/homebrew/opt/ghostscript/lib/libgs.dylib")
}
